\documentclass{beamer}
\usepackage{graphicx}
\usepackage{cancel}

\title[]{Succeeding without a plan}
\subtitle{Saying \underline{yes} to opportunities}
\author{Ben Morcos}
\date{March 16, 2019}

\usetheme{SimplePurple}
\begin{document}

    \frame {
        \titlepage
    }

    \frame {
        \frametitle{Life after school}

        \begin{center}
            {\Huge \textbf{Congratulations!}}
        \end{center}
        \vfill

        \pause
        \begin{itemize}[<+->]
            \item You magically have all the answers now!
        \end{itemize}

    }

    \frame {
        \frametitle{What next?}

        \begin{itemize}
            \item Get a job?
            \item Grad school?
            \item Travel?
            \item Do something completely unrelated?
        \end{itemize}
        \vfill
        \pause
        \begin{center}
            {\Large \textbf{It's okay to not have a plan}}
        \end{center}

    }

    \frame {
        \frametitle{About me}

        \begin{itemize}
            \item Graduated with Tron16
            \item Working at Applied Brain Research
            \item Doing a part-time MASc. in ECE
        \end{itemize}
    }

    \frame {
        \frametitle{What I do now}
        \framesubtitle{Applied Brain Research}

        \alert{Applied Brain Research} is a startup out of the Computational Neuroscience Research Group at UW.

        \pause

        \begin{itemize}
            \item Collection of PhDs with backgrounds in neural networks, robotics, sortware, etc.
            \item Developing new applications in adaptive robotics, machine vision, language processing, etc.
            \item Maintain \alert{Nengo}, a \emph{neural compiler}
        \end{itemize}

    }

    \frame {
        \frametitle{What I do now}
        \framesubtitle{Neuromorphics?}

        I have the fancy job title of \alert{Neuromorphic Engineer}.
        \vfill
        \pause

        \begin{overprint}
            \onslide<2>
                What is \emph{neuromorphic}?
                \begin{itemize}
                    \item Alternative to classic Von Neumann architecture
                    \begin{itemize}
                        \item Inspired by the brain
                    \end{itemize}
                    \item Several neuromorphic chips exist, but aren't accessible
                    \begin{itemize}
                        \item SpiNNaker, Braindrop, True North, Loihi
                    \end{itemize}
                \end{itemize}
            \onslide<3>
                What do I do?
                \begin{itemize}
                    \item Work with FPGAs to design pseudo-neuromorphic chips
                    \begin{itemize}
                        \item Low cost, available commercially
                    \end{itemize}
                    \item Connect FPGA implementation to Nengo frontend
                    \begin{itemize}
                        \item Easy to use
                    \end{itemize}
                \end{itemize}
        \end{overprint}

    }

    \frame {
        \frametitle{What I do now}
        \framesubtitle{MASc.}

        I'm also working with \alert{Dr. Nachiket Kapre} in the Waterloo \alert{Configurable Architectures Group}.

        \begin{itemize}
            \item I'm lucky that research at my job is my thesis work (mostly)
            \item Hoping to finish this summer
        \end{itemize}

    }

    \frame {
        \frametitle{What I do now}
        \framesubtitle{How did this happen?}

        How did I get here without a plan?

    }

    \frame {
        \frametitle{In the beginning}
        \framesubtitle{Engineering}

        Growing up I liked \alert{building things} and \alert{science} so engineering seemed like a good choice.
        \vspace{1em}
        \pause

        More mechanically inclined, I've never coded in my life... \\
        ...but \alert{mechatronics} sounds super interesting, so why not?

    }

    \frame {
        \frametitle{Undergrad}
        \framesubtitle{Mechatronics}

        Essentially no elective for the first 3 years.

        \begin{itemize}
            \item Awesome, no decisions!
        \end{itemize}

    }

    \frame {
        \frametitle{Undergrad}
        \framesubtitle{Co-op placements}

        I was all over the place, no idea what I wanted

        \begin{itemize}
            \item Heavy industry
            \item Medical
            \item Automotive
            \item Microelectronics
        \end{itemize}

        \pause
        \vfill
        \begin{center}
            \textbf{This showed me what I didn't want to do}
        \end{center}

    }

    \frame {
        \frametitle{Undergrad}
        \framesubtitle{Electives}

        Alright, time to try some new topics
        \begin{itemize}
            \item Machine Learning
            \item Neural Networks
            \item Philosophy
        \end{itemize}

        \pause
        \vfill
        I actually \alert{attended class} for these! This is probably the right direction.

    }

    \frame {
        \frametitle{After undergrad}
        \framesubtitle{Actually more like March}


        \begin{itemize}
            \item Planned some trips
            \item Had some interviews
            \item Considered non-engineering work
            \item<2> \alert{Still no real long-term plan}
        \end{itemize}

    }

    \frame {
        \frametitle{After undergrad}
        \framesubtitle{Starting at ABR}

        One of my professors, \alert{Dr. Chris Eliasmith}, invited me to interview at his company...
        \vfill
        \pause

        Why not? I like the class -- say \alert{\underline{yes}} to opportunities!

        \begin{itemize}
            \item Interesting research area
            \item Not a position that will get boring
            \item I like the people
        \end{itemize}

    }

    \frame {
        \frametitle{Working at ABR}
        \framesubtitle{I have no idea what I'm doing}

        I accepted the job and began working with FPGAs, despite directly saying \alert{hardware is my weakest area}!

        \vfill
        I quickly figured out:
        \begin{itemize}[<+->]
            \item This is hard
            \item Epiphany -- that's what that class was about!
            \item I have no idea what I'm doing
        \end{itemize}
    }

    \section{1 Year Later}

    \frame {
        \frametitle{Working at ABR}
        \framesubtitle{I have \xcancel{no} \emph{some} idea what I'm doing}

        I managed to make some progress and have some basic hardware functional!

    }

    \frame {
        \frametitle{Grad school}
        \framesubtitle{How did this happen?}

        There is a seminar on campus about putting neural networks on FPGA. How serendipitous!

        \pause
        \vfill
        Basically,
        \begin{itemize}
            \item Dr. Kapre was a new professor at UW
            \item He gives a seminar uncannily similar to my work
            \item Say \alert{\underline{yes}} to opportunities!
            \begin{itemize}
                \item Oops I'm now doing a master's degree now?
            \end{itemize}
        \end{itemize}


    }

    \frame {
        \frametitle{Here we are}

        \begin{itemize}[<+->]
            \item I have a job I didn't know existed
            \item Working in a subject I barely understood in school
            \item Amongst people far smarter than me
            \item And, somehow I'm back in school
        \end{itemize}

    }

    \frame {
        \frametitle{Remember}
        \framesubtitle{Advice from my father}

        Ask yourself three things:
        \pause
        \begin{enumerate}[<+->]
            \item Do you like the people you work with?
            \item Are you engaged in your work?
            \item Do you have enough money to be comfortable?
        \end{enumerate}

    }

    \frame {
        \frametitle{Remember}
        \framesubtitle{Advice from me}

        \begin{itemize}[<+->]
            \item You don't need to have a concrete plan
            \begin{itemize}
                \item but you should have a general direction
            \end{itemize}
            \item Start saying \alert{\underline{yes}} to opportunities!
            \begin{itemize}
                \item even if you're unsure or underqualified
            \end{itemize}
            \item Your dream job might not exist yet!
        \end{itemize}

        \vfill
        \begin{center}
            \onslide<+->
            {\Large\textbf{Try and take life a little less seriously!}}
        \end{center}

    }

\end{document}
